---
title: "MovieVerse Data Insights"
author: "Data Analyst Team of MovieVerse"
date: "`r Sys.Date()`"
output: html_document
---

## Introduction

This document provides insights into movie ratings and genre popularity based on the MovieVerse dataset. We aim to uncover patterns that could inform future movie recommendations and understand current trends in movie preferences.

## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
```

## Data Import

First, let's load the movie data. This dataset includes movie titles, genres, and ratings.

```{r data-import}
movies <- read.csv("movies.csv")
```

## Data Overview

Let's take a quick look at the structure of our dataset.

```{r data-overview}
str(movies)
head(movies)
```

## Rating Distribution

Understanding the distribution of movie ratings can provide insights into general viewer satisfaction.

```{r rating-distribution}
ggplot(movies, aes(x=rating)) +
  geom_histogram(binwidth = 0.5, fill="steelblue", color="black") +
  labs(title="Distribution of Movie Ratings", x="Rating", y="Frequency") +
  theme_minimal()
```

## Genre Popularity

Next, let's examine which genres are most popular among our collection of movies.

```{r genre-popularity}
movies %>%
  separate_rows(genre, sep=",") %>%
  count(genre) %>%
  ggplot(aes(x=reorder(genre, n), y=n, fill=genre)) +
  geom_col() +
  coord_flip() +
  labs(title="Popularity of Movie Genres", x="Genre", y="Number of Movies") +
  theme_minimal() +
  scale_fill_viridis_d()
```

## Budget vs. Revenue

It's also interesting to explore the relationship between a movie's budget and its revenue.

```{r budget-revenue}
movies <- movies %>%
  mutate(log_budget = log(budget + 1), log_revenue = log(revenue + 1))

ggplot(movies, aes(x=log_budget, y=log_revenue)) +
  geom_point(aes(color=rating), alpha=0.5) +
  geom_smooth(method="lm", se=FALSE, color="blue") +
  labs(title="Budget vs. Revenue (Log Scales)", x="Log of Budget", y="Log of Revenue", color="Rating") +
  theme_minimal()
```

## Conclusion

This exploratory analysis has provided valuable insights into movie ratings, genre popularity, and the financial aspects of movie production. These insights can help guide decision-making for future movie production and recommendation systems.
